\centre \chapter{Introduction}
\section{Problem Definition}
\par This project plans to take working and understanding methods of various industries up a notch. This is to be achieved with the help of converting all desired speech to 3D scenes almost ’as-is’. The goal is to improvise working, discussion and learning of education, corporate and creative industries by providing a better, and more attractive and interactive, platform to express thoughts and explain concepts, along with the ability to design various kinds of layouts and blueprints using only words. The end-game is for the users to be able to” Literally paint the picture with words”.
\section{Motivation}
The idea of this project was the result of a continuous observation of currently opted systems for expressing, understanding, learning knowledge and designing various designs. The current systems and methods were fading, resulting in monotony and ineffectiveness. Thus, the desire to make it all better was key for thinking and going forward with the project.
\section{Scope}
Ability to achieve near real-time 3D scene generation for provided speech, for various purposes and industries, with the help of a large collection of image and scene files. The users will also be able to view the generated scene from any angle (360 degree rotation). The project will achieve near-perfection status once it is able to learn common usual activities and usages in order to provide suggestions and make predictions using Artificial Intelligence.
\section{Salient contribution}
Creating a dent in industries like education, corporate and creative, by drastically changing the way people express, understand and design their thoughts or work. The system is intended to be dynamic, generating 3D scenes on-the-go and as-is, with the ability to learn user habits for future benefits.
\section{Organization of the Synopsis}
The synopsis consists of introduction to the project. It contains the project management plan defining the tasks, descriptions, risks and schedule. It includes requirements for the project consisting of requirement specifications, UI, hardware and software requirements, and product attributes along with database requirements. It then contains the design description consisting of requirement trace-ability matrix, system architecture and UI. It also contains test plan and data for the project, along with test cases, approach and features to be, or not to be, tested.
